---
title: "CO2 emission"
output: html_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
source("./scripts/Summary_data.R")
source("./scripts/Summary_table.R")
source("./scripts/chart1.R")
source("./scripts/chart2.R")
source("./scripts/chart3.R")

```





## Summary Table

This table talks about the growth rate of population
lifetime, and CO2 emission for all the countries in
the world from 1949 to 2014. With sum of the all diff,
we get overall change for 1949 to 2014. Divided by the time
interval, we get the the rate of change of Population, life_expectancy,
and CO2 emission from 1949 to 2014. <br>
Important info: <br>
1. Based on the table, it is clear to see that the population
change rate is directly proportional to the CO2 emission rate. <br>
2. Compare to two other columns(population change rate and
CO2 emission change rate), the lifetime doesn't change that
much with a less than one year increase each year from
1949 to 2014. <br>



```{r echo=FALSE, warning=FALSE}

Summary_table

```





## Effect of CO2 Emissions on Life Expectancy
``` {r echo=FALSE, warning=FALSE}
chart2

```

This shows the yearly change in the relationship between <br>
a countries emission rate, and the quality of life of said <br>
countries citizens (under the reasonable assumption that life <br> 
expectancy is an apposite indicator of overall quality of life). <br>
As shown above the lifespan of the citizens increases as the <br>
country emits more greenhouse gases, meaning that it is in <br>
the direct interest of a country and its citizens to industrialize <br>
and pollute the environment; as not doing so would stymie economic and social progress.
<br>
Data comes from two sources: the Carbon Dioxide Information <br>
Analysis Center (CDIAC), and the World Bank. <br>
The solid lines track a countries emission of greenhouse gases (in million metric tons of CO2). <br>
The dashed life tracks the average life expectancy at birth. 
