---
title: "CO2 emission"
output:
  html_document: default
runtime: shiny
---

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
source("./scripts/Summary_info.R")
source("./scripts/Summary_table.R")
source("./scripts/chart1.R")
source("./scripts/chart2.R")
source("./scripts/chart3.R")

```

## Domain of Interest

We choose CO2 emission as our field of study due to our shared interest in climate change and natural environments. At the same time, we think the natural environment plays an important role in our daily life, so we want to get to know more about the correlation between humans and the environment.

## Source of data:
[Data on co2 emission per country from the CDIAC](https://datahub.io/core/co2-fossil-by-nation#readme):** <br>

## Summary Information

Based on the dataset, the country with the highest total CO2 emission from 1800 to 2016 is `r highest_Co2_country$Country`. <br>
The year with the highest total emission is `r highest_Co2_year$Year` with total emission `r highest_Co2_year$total_emission`. <br>
The country with the highest life expectancy growth rate is `r highest_life_rate_country$Country` with growth rate `r highest_life_rate_country$Life_rate`. <br>
The country with the highest population growth is `r highest_Pop_rate_country$Country`. <br>
The country with the highest HDI growth rate is `r highest_HDI_rate_country$Country`. <br>


## Summary Table

This table talks about the growth rate of population
lifetime, and CO2 emission for all the countries in
the world from 1949 to 2014. With sum of the all diff,
we get overall change for 1949 to 2014. Divided by the time
interval, we get the the rate of change of Population, life_expectancy,
and CO2 emission from 1949 to 2014. <br>
Important info: <br>
*1. Based on the table, it is clear to see that the population
change rate is directly proportional to the CO2 emission rate. <br>
*2. Compare to two other columns(population change rate and
CO2 emission change rate), the lifetime doesn't change that
much with a less than one year increase each year from
1949 to 2014. <br>

```{r echo=FALSE, warning=FALSE}

kable(Summary_table,
      row.names = FALSE)

```


## Chart 1

This chart was intended to show the relationship between
CO2 emissions per capita and GDP per capita for
different countries in the world from 1800-2016. <br>
Important info: <br>
*1. It is pretty obvious that the U.S. always in a
very high position on both GDP per capita and
CO2 emission per capita after 1900. <br>
*2. Many current developed countries like
the U.S. and the U.K. have much
higher CO2 emissions in 20th century than in
21st century. <br>

```{r echo=FALSE, warning=FALSE}

chart1

```


## Chart 2

## Effect of CO2 Emissions on Life Expectancy
``` {r echo=FALSE, warning=FALSE}
chart2
```

This shows the yearly change in the relationship between <br>
a countries emission rate, and the quality of life of said <br>
countries citizens (under the reasonable assumption that life <br> 
expectancy is an apposite indicator of overall quality of life). <br>
As shown above the lifespan of the citizens increases as the <br>
country emits more greenhouse gases, meaning that it is in <br>
the direct interest of a country and its citizens to industrialize <br>
and pollute the environment; as not doing so would stymie economic and social progress.
<br>
Data comes from two sources: the Carbon Dioxide Information <br>
Analysis Center (CDIAC), and the World Bank. <br>
The solid lines track a countries emission of greenhouse gases (in million metric tons of CO2). <br>
The dotted life tracks the average life expectancy at birth. 


## Chart 3

I decided to create a scatterplot with the average human development index number (from 0 to 1) of a country for each country from 1990-2017 on the x axis and the same country's average percent renewable energy from 1990-2017 on the y axis. I believed that the amount of wealth and development a country has would directly correlate with the ratio of renewable energy used in that country and a correlation scatter plot would be the best way to display that. However, I did not realize that there would be an inverse correlation- that is, the lower a country's HDI, the more % renewable energy that country uses. At first, this was surprising, but it later made sense to me, because wealthier countries like the United States tend to be more industrialized
and therefore output more Co2 than third world countries that don't have factories or mass production. <br>

``` {r echo=FALSE, warning=FALSE}

chart3

```
