---
title: "CO2 emission"
output:
  html_document: default
---

```{r echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
source("./scripts/Summary_info.R")
source("./scripts/Summary_table.R")
source("./scripts/chart1.R")
source("./scripts/chart2.R")
source("./scripts/chart3.R")

```





## Summary Table

This table talks about the growth rate of population
lifetime, and CO2 emission for all the countries in
the world from 1949 to 2014. With sum of the all diff,
we get overall change for 1949 to 2014. Divided by the time
interval, we get the the rate of change of Population, life_expectancy,
and CO2 emission from 1949 to 2014. <br>
Important info: <br>
*1. Based on the table, it is clear to see that the population
change rate is directly proportional to the CO2 emission rate. <br>
*2. Compare to two other columns(population change rate and
CO2 emission change rate), the lifetime doesn't change that
much with a less than one year increase each year from
1949 to 2014. <br>

```{r echo=FALSE, warning=FALSE}

kable(Summary_table,
      row.names = FALSE)

```


## Chart 1

This chart was intended to show the relationship between
CO2 emissions per capita and GDP per capita for
different countries in the world from 1800-2016. <br>
Important info: <br>
*1. It is pretty obvious that the U.S. always in a
very high position on both GDP per capita and
CO2 emission per capita after 1900. <br>
*2. Many current developed countries like
the U.S. and the U.K. have much
higher CO2 emissions in 20th century than in
21st century. <br>

```{r echo=FALSE, warning=FALSE}

chart1

```


## Chart 2

